---
title: "Function documentation"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

<!--
 For each fo the function you need, add FUSEN chunk through the Rstudio add-in " add {fusen} chunks"
 -->

# Protection Monitoring

Typically the content of a Protection Monitoring Dashboard allows to quickly identify the situation of basic rights in order to pilot the activities on the ground. It should complement (and not replace!) an in-depth protection analysis based on the protection risk equation. It could include the following default charts:

## 1. Exposure:  plot_vulnerable_profile

Stacked bar chart displaying the percentage or distribution of different vulnerable populations (e.g., children, women, elderly, disabled) affected by protection concerns.
 
```{r function-plot_vulnerable_profile}
#' Title
#' 
#' Vulnerable Populations: Stacked bar chart displaying the percentage or distribution of different vulnerable populations (e.g., children, women, elderly, disabled) affected by protection concerns.
#' 
#' @parama vulnerable_data vulnerable_data 
#' 
#' @return ggplot2 object
#' @import ggplot2
#' @importFrom unhcrthemes theme_unhcr
#' @export
plot_vulnerable_profile <- function(vulnerable_data){
  
  # Create a stacked bar chart
p <- ggplot2::ggplot(vulnerable_data, 
                     ggplot2::aes(x = "", y = Percentage, fill = Population_Group)) +
  ggplot2::geom_bar(stat = "identity", width = 1) +
  ggplot2::geom_text(
    ggplot2::aes(label = paste0(Percentage, "%")), 
    position = ggplot2::position_stack(vjust = 0.5), 
    color = "white", size = 4) +
  ggplot2::coord_polar(theta = "y") +
  ggplot2::labs(title = "Distribution of Vulnerable Populations",
       x = NULL,
       y = NULL) +
  unhcrthemes::theme_unhcr() +
  ggplot2::theme(legend.position = "bottom")

return(p)
    
}
```
  
```{r example-plot_vulnerable_profile}
 
# Create dummy data
vulnerable_data <- data.frame(
  Population_Group = c("Children", "Women", "Elderly", "Disabled"),
  Percentage = c(30, 40, 20, 10)
)

# Calculate cumulative percentage for stacked bar chart
vulnerable_data$Cumulative_Percentage <- cumsum(vulnerable_data$Percentage)




plot_vulnerable_profile(vulnerable_data)
```
  
```{r tests-plot_vulnerable_profile}
test_that("plot_vulnerable_profile works", {
  expect_true(inherits(plot_vulnerable_profile, "function")) 
})
```


## 2. Thread: plot_incident_trend

Incident Types and Frequency: Line chart illustrating the trend in the frequency of of different types of protection incidents (e.g., violence, exploitation, discrimination) over time, allowing for identification of spikes or patterns.

```{r function-plot_incident_trend}
#' plot_incident_trend
#' 
#' Incident Types and Frequency: Line chart illustrating the trend in the frequency of of different types of protection incidents (e.g., violence, exploitation, discrimination) over time, allowing for identification of spikes or patterns.
#' 
#' @param incident_data incident_data
#' 
#' 
#' @return ggplot2 object
#' @import ggplot2
#' @importFrom unhcrthemes theme_unhcr
#' @export
plot_incident_trend <- function(incident_data){
  
  # Create a line chart
  p <- ggplot2::ggplot(incident_data,
                       ggplot2::aes(x = Time_Period,
                                    y = Incident_Count)) +
    ggplot2::geom_line() +
    ggplot2::geom_point() +
    ggplot2::labs(title = "Trend in Frequency of Protection Incidents",
                  x = "Time Period",
                  y = "Incident Count") +
    unhcrthemes::theme_unhcr()  
    
    return(p)
    
}
```
  
```{r example-plot_incident_trend}


#  Line chart illustrating the trend in the frequency of protection incidents over time, allowing for identification of spikes or patterns
# Create dummy data
incident_data <- data.frame(
  Time_Period = seq(as.Date("2023-01-01"), as.Date("2023-12-31"), by = "month"),
  Incident_Count = c(20, 25, 30, 35, 40, 50, 55, 60, 65, 70, 75, 80)
)

plot_incident_trend(incident_data)
```
  
```{r tests-plot_incident_trend}
test_that("plot_incident_trend works", {
  expect_true(inherits(plot_incident_trend, "function")) 
})
```
  



## 3. Coping: Response Coverage: plot_response_coverage

Donut chart showcasing the coverage and reach of protection interventions by different implementing organizations or sectors.
    
```{r function-plot_response_coverage}
#' plot_response_coverage
#' 
#' Donut chart showcasing the coverage and reach of protection interventions by different implementing organizations or sectors.
#' 
#' @param interventions_data interventions_data
#' @return ggplot2 object
#' @import ggplot2
#' @importFrom unhcrthemes theme_unhcr
#' @export
plot_response_coverage <- function(interventions_data){
  
  # Sort the data by coverage
interventions_data <- interventions_data[order(interventions_data$Coverage, decreasing = TRUE), ]

# Calculate the percentages
interventions_data$Percentage <- interventions_data$Coverage / sum(interventions_data$Coverage) * 100

# Create a donut chart
p <- ggplot2::ggplot(interventions_data, 
                     ggplot2::aes(x = "", 
                                  y = Percentage, 
                                  fill = Organization)) +
  ggplot2::geom_bar(stat = "identity", width = 1, color = "white") +
  ggplot2::coord_polar("y", start = 0) +
  ggplot2::labs(title = "Coverage of Protection Interventions",
       x = NULL,
       y = NULL) +
  ggplot2::scale_fill_manual(values = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728")) +
  ggplot2::theme(legend.position = "right") +
    unhcrthemes::theme_unhcr()  

return(p)

    
}
```
  
```{r example-plot_response_coverage}
interventions_data <- data.frame(
  Organization = c("Organization A", "Organization B", "Organization C", "Organization D"),
  Coverage = c(30, 20, 25, 25)
)

plot_response_coverage(interventions_data)
```
  
```{r tests-plot_response_coverage}
test_that("plot_response_coverage works", {
  expect_true(inherits(plot_response_coverage, "function")) 
})
```
  

##  4. Compliance with Protection Standards: plot_protection_standard

Radar chart comparing the adherence to different protection standards (e.g., human rights principles, international humanitarian law) by various implementing actors or sectors.

    
```{r function-plot_protection_standard}
#' plot_protection_standard
#' 
#' Radar chart comparing the adherence to different protection standards (e.g., human rights principles, international humanitarian law) by various implementing actors or sectors.
#' 
#' @param actors_data actors_data
#' @return ggplot2 object
#' @import ggplot2
#' @importFrom ggradar ggradar
#' @importFrom unhcrthemes theme_unhcr
#' @export
plot_protection_standard <- function(actors_data){
    # Create a function to normalize the values between 0 and 1
normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}

# Normalize the data
actors_data[, -1] <- apply(actors_data[, -1], 2, normalize)
# devtools::install_github("ricardo-bion/ggradar")
p <- ggradar::ggradar(actors_data) +
    unhcrthemes::theme_unhcr()  

return(p)

}
```
  
```{r example-plot_protection_standard}
# Create dummy data
# Data Protection and Confidentiality
# 

actors_data <- data.frame(
  Actor = c("Actor A", "Actor B", "Actor C", "Actor D", "Actor E"),
  Human_Rights = c(4, 3, 5, 2, 4),
  Humanitarian_Law = c(3, 4, 2, 5, 3)
)

plot_protection_standard(actors_data)
```
  
```{r tests-plot_protection_standard}
test_that("plot_protection_standard works", {
  expect_true(inherits(plot_protection_standard, "function")) 
})
```

## 5. Protection Advocacy Challenges: plot_advocacy_steps

Gantt chart depicting the timeline of identified advocacy and the status of efforts to address them, allowing for tracking progress and resolution.
    
```{r function-plot_advocacy_steps}
#' plot_advocacy_steps
#' 
#' Gantt chart depicting the timeline of identified advocacy and the status of efforts to address them, allowing for tracking progress and resolution.
#' 
#' @param challenges_data challenges_data
#' @return ggplot2 object
#' @import ggplot2 
#' @import dplyr
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
plot_advocacy_steps <- function(challenges_data){
    # Sort challenges data by start date
challenges_data <- challenges_data |> 
                     dplyr::arrange(Start_Date)

# Create a Gantt chart
p <- ggplot2::ggplot(challenges_data) +
  ggplot2::geom_segment(
    ggplot2::aes(x = Start_Date, 
                   xend = End_Date, 
                   y = Challenge, 
                   yend = Challenge, 
                   color = Status), 
               size = 10) +
  ggplot2::labs(title = "Timeline of Identified Challenges",
       x = "Timeline",
       y = NULL) +
  ggplot2::scale_color_manual(values = c("In Progress" = "#FFA500", "Completed" = "#008000")) +
  ggplot2::theme(axis.text.y = ggplot2::element_blank(),
        axis.ticks.y = ggplot2::element_blank(),
        panel.grid.major.y = ggplot2::element_blank(),
        panel.grid.minor.y = ggplot2::element_blank())+
   unhcrthemes::theme_unhcr()  

return(p)

}
```
  
```{r example-plot_advocacy_steps}
# Create dummy data

  
    
challenges_data <- data.frame(
  Challenge = c("Access Constraints - security concerns, government restrictions, or logistical obstacles",
                "Gender-Based Violence (GBV) - establish safe spaces, provide support services, and raise awareness", 
                "Child Protection - exploitation, abuse, and recruitment into armed groups ",
                "Land disputes & forced evictions", 
                "Community Engagement: Building trust and effectively engaging with affected communities. involve local communities in decision-making processes to ensure that their needs and concerns are heard and addressed"),
  Start_Date = as.Date(c("2023-01-01", "2023-02-01", "2023-03-01", "2023-04-01", "2023-04-01")),
  End_Date = as.Date(c("2023-03-31", "2023-05-31", "2023-06-30", "2023-09-30", "2023-09-30")),
  Status = c("Overcome", "Critical", "Increasing", "In Progress", "In Progress")
)

plot_advocacy_steps(challenges_data)
```
  
```{r tests-plot_advocacy_steps}
test_that("plot_advocacy_steps works", {
  expect_true(inherits(plot_advocacy_steps, "function")) 
})
```
  


## 6. Key Performance Indicators (KPIs): plot_kpi

 
    
```{r function-plot_kpi}
#' plot_kpi
#' 
#' Highlighted numbers specific KPIs related to the protection response
#'  (e.g., number of cases resolved, number of survivors accessing 
#'  support services).
#' @description ## https://datavizcatalogue.com/methods/bullet_graph.html
#'   In a Bullet Graph, the main data value is encoded by length with the bar in the 
#'  centre of the chart, which is known as the Feature Measure. The line marker that 
#'  runs perpendicular to the orientation of the graph is known as the Comparative 
#'  Measure and is used as a target marker to compare against the Feature Measure 
#'  value. So if the main bar has passed the position of Comparative Measure, you 
#'  know you've hit your goal.

#'  The segmented coloured bars behind the Feature Measure are used to display 
#'  qualitative range scores. Each colour shade (the three shades of grey in the
#'  example above) are used to assign a performance range rating. So for example,
#'  poor, average and great. When using Bullet Graphs, it's ideal to keep the 
#'  maximum number of performance ranges to five. 
#'
#' @param data RBM QA dataset - expect a few pre-defined variables to works well..
#' @param thisind which indicator to chart
#'
#' @importFrom unhcrthemes theme_unhcr
#'
#' @return frame with all compass indicators
#' 
#' @export
#'
rbm_bullet <- function(data, thisind){
  # thisind <-  "OA1-1.2"
  #names(data)
  thisdata1 <- data |>
             dplyr::filter(Ind_id == thisind) |>
             # dplyr::select(Operation, country,Ind_clean, population_type_clean, population_label, 
             #               data_source, additional_data_source, data_sources_comment,
             #               baseline_2022_percent,
             #               actual_2022_percent, op_target_2022, op_target_2023, ol_target_2022, 
             #               show_as, reverse, area, results_level,
             #               threshold_red, threshold_orange, threshold_green, reverse, standard_direction,
             #               disag_PopulationType, disag_Age, disag_Gender, disag_Disability, 
             #               disag_Origin, disag_Nation)  |>
            dplyr::mutate(country = stringr::str_replace(country, " \\(Bolivarian Republic of\\)", "")) |>
            dplyr::distinct() |>
             dplyr::mutate(additional_data_source = stringr::str_replace_all(additional_data_source,
                                                                             "https://", " " ) ) |>
            dplyr::rename(target = op_target_2022, 
                          baseline = baseline_2022_percent, 
                          actual = actual_2022_percent ) |>  
            dplyr::mutate(additional_data_source = substr(additional_data_source, 0 , 50)) |>
            tidyr::unite(col =  "data_info", 
              all_of( c("data_source", "additional_data_source") ), 
                      na.rm = TRUE, 
                      sep = "<br> ",
                 remove = FALSE) |>
            ## Trying to sanitize to get rid of..
            ## Error: gridtext has encountered a tag that isn't supported yet: <a>
            # Only a very limited number of tags are currently supported.
            
            dplyr::mutate(data_info = stringr::str_replace_all(data_info, "https://", " " ) ) |>
            dplyr::mutate(data_info = stringr::str_replace_all(data_info, "www.", " " ) ) |>
    
            dplyr::mutate( group = as.character(glue::glue("{country}/{population_type_clean}") ) ) |>
            dplyr::mutate( operation = as.character(glue::glue("<b>{country}/{population_type_clean}</b><br> <i>({data_info} )</i>") ) ) |>
            #dplyr::arrange(desc(actual))
            dplyr::group_by(country) |>
            dplyr::arrange(desc( actual), .by_group=TRUE ) |> 
            dplyr::ungroup(country) 
  
    ## We keep only when there's value for plotting!
    thisdata <- thisdata1   |>
            dplyr::filter( !(is.na(actual))) 
    #thisdata$operation
    
    nline <- nrow(thisdata)
    indname <- thisdata |>
              dplyr::distinct(Ind_clean) |>
              dplyr::pull()
    standard_direction <- thisdata |>
              dplyr::distinct(standard_direction) |>
              dplyr::pull()
    reverse <- thisdata |>
              dplyr::distinct(reverse) |>
              dplyr::pull()
    show_as <- thisdata |>
              dplyr::distinct(show_as) |>
              dplyr::pull()
    area <- thisdata |>
              dplyr::distinct(area) |>
              dplyr::pull()
    ## levels(as.factor(data$results_level))
    results_level <- thisdata |>
              dplyr::distinct(results_level) |>
              dplyr::pull()

    
## case there's no data at all 

if( nrow(thisdata) == 0) {
  info <-  paste0("There\'s no recorded indicator value \n", thisind)
  p <- ggplot() +  annotate("text",  x = 1, y = 1, size = 12,  
                            label = info ) +  theme_void() 
  
  } else if(nrow(thisdata)> 0) {
      ## and now the plot
    p <- ggplot(  data = thisdata ) +
      coord_flip() 
    
    ## Background with color band! 
    if( standard_direction == "more_or_equal") {
      maxgreen <- max(thisdata$threshold_green)
      maxorange <- max(thisdata$threshold_orange)
      maxred <- max(thisdata$threshold_red)
      yaxistext <- paste0("\n (as ", show_as, ") Actual value = horizontal blue line. \n Baseline = black vertical line | Target = vertical grey line")
      p <- p +
        geom_col( aes(x = reorder(operation, actual) , y = threshold_green),
                  fill = "#069C56", width = 0.6, alpha = 0.4  ) +
        geom_col( aes(x = reorder(operation, actual), y = threshold_orange),
                  fill = "#FF980E", width = 0.6,  alpha = 0.4 ) +
        geom_col(  aes(x = reorder(operation, actual), y = threshold_red),
                   fill = "#D3212C", width = 0.6, alpha = 0.4 )
    }  else if ( standard_direction == "less_or_equal") { 
      
      maxgreen <- max(thisdata$threshold_green)
      maxorange <- max(thisdata$threshold_orange)
      maxred <- max(thisdata$threshold_red)
      yaxistext <- paste0("\n (as ", show_as, ") Actual value = horizontal blue line. \n Baseline = black vertical line | Target = vertical grey line")
      p <- p   +
        geom_col(  aes(x = reorder(operation, actual), y = threshold_red),
                   fill = "#D3212C", width = 0.6, alpha = 0.4 )+
        geom_col( aes(x = reorder(operation, actual), y = threshold_orange),
                  fill = "#FF980E", width = 0.6,  alpha = 0.4 )+
        geom_col( aes(x = reorder(operation, actual) , y = threshold_green),
                  fill = "#069C56", width = 0.6, alpha = 0.4  )
    }
    
    p <- p  +
      geom_errorbar(  aes(x = reorder(operation, actual), ymin = baseline, ymax = baseline),
                      color = "black",  width = 0.45,  size = 1) 
    
    ## Add the target and change the color based on the context
    if( results_level == "Outcome" & standard_direction == "No_standard") { 
      p <- p  +
        geom_errorbar(  aes(x = reorder(operation, actual), ymin = target, ymax = target),
                        color = "grey50",  width = 0.45, size = 1  ) 
    }   else  if ( results_level == "Outcome" & standard_direction != "No_standard"){  
      p <- p  +
        geom_errorbar(  aes(x = reorder(operation, actual), ymin = target, ymax = target),
                        color = "white",  width = 0.45, size = 1  )    }     else { }
    
    p <- p  +
      geom_col(   aes(x = reorder(operation, actual), y = actual),
                  fill = "#0072BC",  color = NA,  width = 0.2 ) + 
      geom_text(aes(x = reorder(operation, actual), y = actual,
                    label = round(actual, 1)),
                hjust = 1.5, size = 3,color = "white") 
    
    ## Change scale based on unit!
    if( show_as == "Percent") {
      p <- p +
        # scale_y_continuous( label = scales::label_percent(accuracy = 0,
        #                                 suffix = "%") ) 
        scale_y_continuous( label =  scales::label_number(accuracy = 1,  
                                                          scale_cut = scales::cut_short_scale()) )
    } else {
      p <- p +
        scale_y_continuous( label =  scales::label_number(accuracy = 1,  
                                                          scale_cut = scales::cut_short_scale()) )
    }  
    
    ## Build the axis explanation -- accounting for the unit - 
    # and for the existence of a target in case the indicator is an ooutcome   
    if( results_level == "Outcome" & standard_direction != "No_standard") {
      yaxistext <- paste0("\n (as ",
                          show_as,
                          ") Actual value = horizontal blue line. \n Baseline = black vertical line | Target = vertical white line") 
      
    } else if(results_level == "Outcome" & standard_direction == "No_standard") {
      
      yaxistext <- paste0("\n (as ",
                          show_as,
                          ") Actual value = horizontal blue line. \n Baseline = black vertical line | Target = vertical grey line")
      
    } else if (results_level == "Impact" ) {
      
      yaxistext <- paste0("\n (as ",
                          show_as,
                          ") Actual value = horizontal blue line. \n Baseline = black vertical line")
      
    } 
    
    p <- p +
      unhcrthemes::theme_unhcr(font_size = 12, 
                               rel_small = 6/9,
                               grid = "X", 
                               axis = "y") +
      theme(  axis.text.y = ggtext::element_markdown()) +
      labs( x = "", y =  yaxistext ,
            title = stringr::str_wrap( paste0("RBM Indicator: ", indname) , 60),
            subtitle = stringr::str_wrap( paste0( area, 
                                                  " - Regional Comparison Americas | 2022 Quality Assurance" ) ,
                                          80),
            caption = "Source: UNHCR RBM / Compass ") }
    
}
```
  
```{r example-plot_kpi}

    Percentage of Vulnerable Populations Reached (Threshold: 80%)
        This KPI measures the proportion of the most vulnerable individuals (e.g., children, elderly, disabled) who have received protection services or assistance. The threshold of 80% indicates the goal of reaching a significant majority of those at risk.

    Incident Reporting and Response Time (Threshold: 72 hours)
        This KPI assesses the efficiency of reporting and responding to protection incidents. The threshold of 72 hours indicates that incidents should be reported and responded to within three days of occurrence.

    Access to Safe Shelter (Threshold: 95%)
        Measures the percentage of affected populations who have access to safe and adequate shelter. The threshold of 95% indicates a high standard for shelter provision.

    # Child Protection Case Closure Rate (Threshold: 90%)
    #     This KPI tracks the rate at which child protection cases are successfully resolved and closed. A threshold of 90% indicates the aim to resolve the majority of cases.
    # 
    # Percentage of Gender-Based Violence Survivors Receiving Support (Threshold: 80%)
    #     Measures the percentage of survivors of gender-based violence who receive essential support services. The threshold of 80% represents the goal to provide assistance to the majority of survivors.
    # 
    # Community-Based Protection Mechanisms (Threshold: 100%)
    #     This KPI assesses the establishment and functionality of community-based protection structures or committees. The threshold of 100% indicates the aim to have such mechanisms in place in all relevant communities.
    # 
    # Child Enrollment in Education Programs (Threshold: 90%)
    #     Measures the percentage of children in affected areas who are enrolled in formal or non-formal education programs. The threshold of 90% indicates a high enrollment target.
    # 
    # Percentage of Protection Interventions Aligned with Local Context (Threshold: 70%)
    #     Evaluates the extent to which protection interventions are adapted to the specific needs and cultural context of the affected population. The threshold of 70% indicates a significant level of alignment.
    # 
    # Reduction in Protection Incidents (Threshold: 20%)
    #     Measures the percentage decrease in protection incidents (e.g., violence, exploitation) compared to a baseline period. The threshold of 20% indicates the target reduction in incidents.
    # 
    # Community Perception of Safety (Threshold: 70%)
    #     Assesses the percentage of surveyed community members who report feeling safe and protected in their environment. The threshold of 70% represents the desired level of community safety perception.
plot_kpi()
```
  
```{r tests-plot_kpi}
test_that("plot_kpi works", {
  expect_true(inherits(plot_kpi, "function")) 
})
```
  

## 7. Geographic Distribution: plot_geodistrib
    
```{r function-plot_geodistrib}
#' plot_geodistrib
#' 
#' Choropleth map presenting the spatial distribution of protection incidents,
#'  vulnerability, or response activities, allowing for visual identification 
#'  of hotspots or areas in need.
#' 
#' @return ggplot2 object
#' @import ggplot2 
#' @import dplyr
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
plot_geodistrib <- function(){
    p <-  # Bubble choropleth map
ggplot() +
  geom_sf(data = EU_countries, fill = "grey95") +
  geom_sf(
    data = labels_n,
    pch = 21,
    aes(size = n, fill = n),
    col = "grey20") +
  xlim(c(2200000, 7150000)) +
  ylim(c(1380000, 5500000)) +
  scale_size(
    range = c(1, 9),
    guide = guide_legend(
      direction = "horizontal",
      nrow = 1,
      label.position = "bottom")) +
  scale_fill_gradientn(colours = hcl.colors(5, "RdBu",
                                            rev = TRUE,
                                            alpha = 0.9)) +
  guides(fill = guide_legend(title = "")) +
  labs(title = "Airports by Country (2013)",
       sub = "European Union",
       caption = gisco_attributions(),
       size = "") +
  theme_void() +
  theme(legend.position = "bottom")
}
```
  
```{r example-plot_geodistrib}
labels_n <-
  symbol_pos %>%
  left_join(number_airport,
            by = c("CNTR_ID" = "CNTR_CODE")) %>%
  arrange(desc(n))

plot_geodistrib()
```
  
```{r tests-plot_geodistrib}
test_that("plot_geodistrib works", {
  expect_true(inherits(plot_geodistrib, "function")) 
})
```
  


<!--
 below is a default chunk to create and document your run_app function
-->

# run_app


<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_function` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->
    
```{r function-run_app}
#' Run the Shiny Application
#' 
#' 
#' @param onStart A function that will be called before the app is actually run.
#' This is only needed for \code{shinyAppObj}, since in the \code{shinyAppDir}
#' case, a \code{global.R} file can be used for this purpose.

#' @param options Named options that should be passed to the \code{runApp} call
#' (these can be any of the following: "port", "launch.browser", "host", "quiet",
#' "display.mode" and "test.mode"). You can also specify \code{width} and
#' \code{height} parameters which provide a hint to the embedding environment
#' about the ideal height/width for the app.

#' @param enableBookmarking Can be one of \code{"url"}, \code{"server"}, or
#' \code{"disable"}. The default value, \code{NULL}, will respect the setting from
#' any previous calls to  \code{\link[shiny:enableBookmarking]{enableBookmarking()}}. See 
#' #' \code{\link[shiny:enableBookmarking]{enableBookmarking()}}
#' for more information on bookmarking your app.

#' @param uiPattern A regular expression that will be applied to each \code{GET}
#' request to determine whether the \code{ui} should be used to handle the
#' request. Note that the entire request path must match the regular
#' expression in order for the match to be considered successful.
#' 
#' 
#' @param ... arguments to pass to golem_opts.
#' See `?golem::get_golem_options` for more details.
#' @inheritParams shiny::shinyApp
#'
#' @importFrom shiny shinyApp
#' @importFrom golem with_golem_options
#' 
#' @return a shiny app
#' 
#' @export

run_app <- function(
    onStart = NULL,
    options = list(),
    enableBookmarking = NULL,
    uiPattern = "/",
    ...
) {
  with_golem_options(
    app = shinyApp(
      ui = app_ui,
      server = app_server,
      onStart = onStart,
      options = options,
      enableBookmarking = enableBookmarking,
      uiPattern = uiPattern
    ),
    golem_opts = list(...)
  )
}

```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r example-run_app}
# run_app()
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->
 
```{r tests-run_app}
# test_that("run_app works", {
#   expect_true(inherits(run_app, "function")) 
# })
```
  



<!--
 Once you have created your back office functions , run the next chunk to install and package them

# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/function_documentation.Rmd", vignette_name = "Development")
```

